Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-25 doc/paper.tex
some fixes

     Let us suppose we are given a discretization $D(P)$ of the polygon $P$ (with a family of rectangles). Then we relate the OAGP with the known MSC problem.  
     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $p_i$. Note that set $S_i$ includes a point $p_i$ but can also include some other guard $p_j$, $i \neq j$. So, the task of OAPG becomes in finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is 
     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ Since the Integer Programming model for the Set Cover problem is know, it follows that 
     \begin{align}
        &\sum_{i=1}^n x_i \longrightarrow \min \\
        &\mbox{s.t.} \\
        &\sum_{j} a_{ij}x_j \geq 1\ (\forall p_i,1,...,n) \label{eq:const-3}\\
        & x_j \in \{0,1\},  \in V,
     \end{align}
     where 
     $a_{ij} = \begin{cases}
          1, j \in V(j), \\
          0, \mbox{otherwise} 
     \end{cases}$ 
     and $x_i = \begin{cases}
     	 1, \mbox{ if } p_i \in \mathcal{C},\\
     	 0, \mbox{otherwise},
     \end{cases}$ \\
      is a MIP model to solve OAGP. 
     $V(j)$ is a set of all points from $D(P)$ that are visible from vertex $p_j$. Set $Z = \{j \in V\mid x_i=1\}$
     Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.

>>>>

     Let us suppose we are given a discretization $D(P)$ of the polygon $P$ (with a family of rectangles). Then we relate the OAGP with the known MSC problem.  
     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $p_i$. Note that set $S_i$ includes a point $p_i$ which can also include some other guard $p_j$, $i \neq j$. So, the task of OAPG becomes finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is 
     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ Since the Integer Programming model for the Set Cover problem is know, it follows that 
     \begin{align}
        &\sum_{i=1}^n x_i \longrightarrow \min \\
        &\mbox{s.t.} \\
        &\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
        & x_j \in \{0,1\}, j \in V,
     \end{align}
     where 
     $a_{ij} = \begin{cases}
          1, p_i \in V(j), \\
          0, \mbox{otherwise} 
     \end{cases}$ 
     and $x_i = \begin{cases}
     	 1, \mbox{ if } \mbox{ the point } i \in \mathcal{C},\\
     	 0, \mbox{otherwise},
     \end{cases}$ \\
      is a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
     $V(j)$ is a set of all points from $D(P)$ that are visible from vertex $p_j$. Set $Z = \{j \in V\mid x_i=1\}$
     Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
